---
title: "IButtonJul19"
output:
  pdf_document: default
  html_document: default
date: "2023-07-19"
---
# Section 1: K-Mean Cluster Analysis
K-means clustering is the most commonly used unsupervised machine learning algorithm for partitioning a given data set into a set of k groups (i.e. k clusters), where k represents the number of groups pre-specified by the analyst. It classifies objects in multiple groups (i.e., clusters), such that objects within the same cluster are as similar as possible (i.e., high intra-class similarity), whereas objects from different clusters are as dissimilar as possible (i.e., low inter-class similarity). 


```{r, include=FALSE,echo=FALSE}
library(tidyverse)
library(cluster)
library(factoextra)
library(proxy)
library(tidyverse)
library(broom)
library(survey)
library(ggpubr) 
library(ggrepel) 
library(plotrix)
library(knitr)
library(patchwork)
library(pander)
library(gt)
library(readxl)
library(sjPlot)
library(haven)
library(readr)
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE,echo=FALSE}
mydata<-read_excel("ButtonAnalysis.xlsx")
mydata$ButtonNum <- as.character(mydata$ButtonNum)
str(mydata)
mydata <- as.data.frame(mydata)
rownames(mydata) <- c(mydata$ButtonNum)
head(mydata)
mydata <- mydata[,-1]
mydata <- na.omit(mydata)
mydata <- scale(mydata)

```


```{r, include=FALSE,echo=FALSE}
distance <- get_dist(mydata)
view<-fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
view
#fviz_dist: for visualizing a distance matrix
```

Here will group the data into three clusters:
```{r}
k2 <- kmeans(mydata, centers = 6, nstart = 100)
str(k2)
fviz_cluster(k2, data = mydata)
```
## Albedo and Temp
```{r}
albedo5am81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferAlbedo100m, y = AugTemp5am81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
albedo5am81

albedo2pm81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferAlbedo100m, y = AugTemp2pm81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
albedo2pm81

albedo5am82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferAlbedo100m, y = AugTemp5am82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
albedo5am82

albedo2pm82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferAlbedo100m, y = AugTemp2pm82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
albedo2pm82
```

## Landuse and Temp
```{r}
landuse5am81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferLanduse100m, y = AugTemp5am81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
landuse5am81

landuse2pm81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferLanduse100m, y = AugTemp2pm81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
landuse2pm81

landuse5am82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferLanduse100m, y = AugTemp5am82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
landuse5am82

landuse2pm82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferLanduse100m, y = AugTemp2pm82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
landuse2pm82
```
### Elevation and Temp
```{r}
elevation5am81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferElevation100m, y = AugTemp5am81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
elevation5am81

elevation2pm81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferElevation100m, y = AugTemp2pm81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
elevation2pm81

elevation5am82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferElevation100m, y = AugTemp5am82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
elevation5am82

elevation2pm82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferElevation100m, y = AugTemp2pm82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
elevation2pm82
```

## Canopy and Temp
```{r}
canopy5am81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferCanopy100m, y = AugTemp5am81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
canopy5am81

canopy2pm81<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferCanopy100m, y = AugTemp2pm81, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
canopy2pm81

canopy5am82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferCanopy100m, y = AugTemp5am82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
canopy5am82

canopy2pm82<-mydata %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster,
         state = row.names(.)) %>%
  ggplot(aes(x = BufferCanopy100m, y = AugTemp2pm82, color = factor(cluster))) +
  geom_point() +
  geom_text(aes(label = state), vjust = -0.5, hjust = 0.5)
canopy2pm82

```
# Section 2: R-Linear Regression
## Regression (Aug 1 5am)
```{r}
button <- read_excel("ButtonAnalysis.xlsx")
Canopy581 <- lm(AugTemp5am81~BufferCanopy100m, data=button)
CanopyPAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m+BufferAlbedo100m, data=button)
CanopyMAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m*BufferAlbedo100m, data=button)
CanopyPElevation581 <- lm(AugTemp5am81~BufferCanopy100m+BufferElevation100m, data=button)
CanopyMElevation581 <- lm(AugTemp5am81~BufferCanopy100m*BufferElevation100m, data=button)
CanopyPElevationAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m+BufferElevation100m+BufferAlbedo100m, data=button)
CanopyMElevationAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m*BufferElevation100m*BufferAlbedo100m, data=button)
CanopyMElevationPAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m*BufferElevation100m+BufferAlbedo100m, data=button)
CanopyPElevationMAlbedo581 <- lm(AugTemp5am81~BufferCanopy100m*BufferAlbedo100m+BufferElevation100m, data=button)

aic_values <- c(AIC(Canopy581), AIC(CanopyPAlbedo581), AIC(CanopyMAlbedo581), AIC(CanopyPElevation581), AIC(CanopyMElevation581), AIC(CanopyPElevationAlbedo581), AIC(CanopyMElevationAlbedo581), AIC(CanopyMElevationPAlbedo581), AIC(CanopyPElevationMAlbedo581))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table <- data.frame(
  Model = model_names,
  AIC = aic_values) %>%
  arrange(AIC)

print(aic_table)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.

#best fitted model: 
CanopyPElevation581 <- lm(AugTemp5am81~BufferCanopy100m+BufferElevation100m, data=button)

CanopyPElevation581<- tidy(CanopyPElevation581, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyPElevation581 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  kable(digits = 2, format = "markdown", caption = "Table 1: August1 5AM")
```

## Regression (Aug 1 2pm)
```{r}
Canopy281 <- lm(AugTemp2pm81~BufferCanopy100m, data=button)
CanopyPAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m+BufferAlbedo100m, data=button)
CanopyMAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferAlbedo100m, data=button)
CanopyPElevation281 <- lm(AugTemp2pm81~BufferCanopy100m+BufferElevation100m, data=button)
CanopyMElevation281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferElevation100m, data=button)
CanopyPElevationAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m+BufferElevation100m+BufferAlbedo100m, data=button)
CanopyMElevationAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferElevation100m*BufferAlbedo100m, data=button)
CanopyMElevationPAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferElevation100m+BufferAlbedo100m, data=button)
CanopyPElevationMAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferAlbedo100m+BufferElevation100m, data=button)

aic_values2 <- c(AIC(Canopy281), AIC(CanopyPAlbedo281), AIC(CanopyMAlbedo281), AIC(CanopyPElevation281), AIC(CanopyMElevation281), AIC(CanopyPElevationAlbedo281), AIC(CanopyMElevationAlbedo281), AIC(CanopyMElevationPAlbedo281), AIC(CanopyPElevationMAlbedo281))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table2 <- data.frame(
  Model = model_names,
  AIC = aic_values2) %>%
  arrange(AIC)

print(aic_table2)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.

#best fitted model: 
CanopyMElevationAlbedo281 <- lm(AugTemp2pm81~BufferCanopy100m*BufferElevation100m*BufferAlbedo100m, data=button)

CanopyMElevationAlbedo281<- tidy(CanopyMElevationAlbedo281, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyMElevationAlbedo281 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  kable(digits = 2, format = "markdown", caption = "Table 2: August1 2PM")
```
## Regression (Aug 2 5am)
```{r}
Canopy582 <- lm(AugTemp5am82~BufferCanopy100m, data=button)
CanopyPAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m+BufferAlbedo100m, data=button)
CanopyMAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m*BufferAlbedo100m, data=button)
CanopyPElevation582 <- lm(AugTemp5am82~BufferCanopy100m+BufferElevation100m, data=button)
CanopyMElevation582 <- lm(AugTemp5am82~BufferCanopy100m*BufferElevation100m, data=button)
CanopyPElevationAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m+BufferElevation100m+BufferAlbedo100m, data=button)
CanopyMElevationAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m*BufferElevation100m*BufferAlbedo100m, data=button)
CanopyMElevationPAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m*BufferElevation100m+BufferAlbedo100m, data=button)
CanopyPElevationMAlbedo582 <- lm(AugTemp5am82~BufferCanopy100m*BufferAlbedo100m+BufferElevation100m, data=button)

aic_values3 <- c(AIC(Canopy582), AIC(CanopyPAlbedo582), AIC(CanopyMAlbedo582), AIC(CanopyPElevation582), AIC(CanopyMElevation582), AIC(CanopyPElevationAlbedo582), AIC(CanopyMElevationAlbedo582), AIC(CanopyMElevationPAlbedo582), AIC(CanopyPElevationMAlbedo582))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table3 <- data.frame(
  Model = model_names,
  AIC = aic_values3) %>%
  arrange(AIC)

print(aic_table3)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.

#best fitted model: 
CanopyMElevation582 <- lm(AugTemp5am82~BufferCanopy100m*BufferElevation100m, data=button)

CanopyMElevation582<- tidy(CanopyMElevation582, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyMElevation582 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  kable(digits = 2, format = "markdown", caption = "Table 3: August2 5AM")
```
## Regression (Aug 2 2pm)
```{r}
Canopy282 <- lm(AugTemp2pm82~BufferCanopy100m, data=button)
CanopyPAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m+BufferAlbedo100m, data=button)
CanopyMAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferAlbedo100m, data=button)
CanopyPElevation282 <- lm(AugTemp2pm82~BufferCanopy100m+BufferElevation100m, data=button)
CanopyMElevation282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferElevation100m, data=button)
CanopyPElevationAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m+BufferElevation100m+BufferAlbedo100m, data=button)
CanopyMElevationAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferElevation100m*BufferAlbedo100m, data=button)
CanopyMElevationPAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferElevation100m+BufferAlbedo100m, data=button)
CanopyPElevationMAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferAlbedo100m+BufferElevation100m, data=button)

aic_values4 <- c(AIC(Canopy282), AIC(CanopyPAlbedo282), AIC(CanopyMAlbedo282), AIC(CanopyPElevation282), AIC(CanopyMElevation282), AIC(CanopyPElevationAlbedo282), AIC(CanopyMElevationAlbedo282), AIC(CanopyMElevationPAlbedo282), AIC(CanopyPElevationMAlbedo282))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table4 <- data.frame(
  Model = model_names,
  AIC = aic_values4) %>%
  arrange(AIC)

print(aic_table4)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.

#best fitted model: 
CanopyPElevationMAlbedo282 <- lm(AugTemp2pm82~BufferCanopy100m*BufferAlbedo100m+BufferElevation100m, data=button)

CanopyPElevation282<- tidy(CanopyPElevationMAlbedo282, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyPElevation282 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  kable(digits = 2, format = "markdown", caption = "Table 4: August2 2PM")
```

