---
title: "IButton Jul25"
output: html_document
date: "2023-07-26"
---
# Section 1: K-Mean Cluster Analysis
K-means clustering is the most commonly used unsupervised machine learning algorithm for partitioning a given data set into a set of k groups (i.e. k clusters), where k represents the number of groups pre-specified by the analyst. It classifies objects in multiple groups (i.e., clusters), such that objects within the same cluster are as similar as possible (i.e., high intra-class similarity), whereas objects from different clusters are as dissimilar as possible (i.e., low inter-class similarity). 

```{r, include=FALSE,echo=FALSE}
library(tidyverse)
library(cluster)
library(factoextra)
library(proxy)
library(tidyverse)
library(broom)
library(survey)
library(ggpubr) 
library(ggrepel) 
library(plotrix)
library(knitr)
library(patchwork)
library(pander)
library(gt)
library(readxl)
library(sjPlot)
library(haven)
library(readr)
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE,echo=FALSE}
mydata<-read_excel("ButtonAnalysisJuly25.xlsx")
mydata$ButtonNum <- as.character(mydata$ButtonNum)
str(mydata)
mydata <- as.data.frame(mydata)
rownames(mydata) <- c(mydata$ButtonNum)
head(mydata)
mydata <- mydata[,-1]
mydata <- na.omit(mydata)
mydata <- scale(mydata)

```

```{r, include=FALSE,echo=FALSE}
distance <- get_dist(mydata)
view<-fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
view
#fviz_dist: for visualizing a distance matrix
```

Here will group the data into three clusters:
```{r}
k2 <- kmeans(mydata, centers = 6, nstart = 100)
str(k2)
fviz_cluster(k2, data = mydata)
```
```{r}
cluster_assignments <- k2$cluster

# Add the cluster assignments to your original data frame
mydata_with_clusters <- cbind(mydata, Cluster = cluster_assignments)

print(mydata_with_clusters)

# Save the table to a CSV file
write.csv(mydata_with_clusters, "mydata_with_clusters.csv", row.names = FALSE)
```
# Average5am2pm
```{r}
aug <- read_excel("average5am2pm.xlsx")
aug$Date <- factor(aug$Date, levels = unique(aug$Date))

avgtemp <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = average5am), color = "red") +
  geom_line(aes(y = average2pm), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Average August Temperature (ibutton)",
    subtitle = "average5am (red), average2pm (blue), reportC(black)",
    caption = "Figure 1"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

avgtemp <- avgtemp + theme(axis.text.x = element_text(angle = 45, hjust = 1))
avgtemp
```

