---
title: "IButton Jul11"
output: html_document
date: "2023-07-11"
---
```{r library,echo=FALSE, message=FALSE, include=FALSE}
library(tidyverse)  #for data manipulation, exploration, and visualization
library(broom) #turn into tidy dataframe
library(survey) #functions for analyzing complex survey samples
library(ggpubr) #creating and customizing ggplot2-based plot
library(ggrepel) #provides text and label geoms for ggplot2
library(kableExtra) #helps with building complex tables
library(plotrix) #gives a variety of plots
library(knitr) #creating nice reports in RMarkdown
library(patchwork) #
library(pander)
library(gt)
library(readxl)
library(sjPlot)
library(haven)
library(readr)
library(ggplot2)
```

```{r}
aug <- read_excel("August5am.xlsx")
aug2 <- read_excel("August2pm.xlsx")
aug$Date <- factor(aug$Date, levels = unique(aug$Date))
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
```

## Full Shade Grass
### Full Shade Grass 5AM

```{r}
fullgrass <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button3), color = "red") +
  geom_line(aes(y = button16), color = "orange") +
  geom_line(aes(y = button23), color = "green") +
  geom_line(aes(y = button25), color = "cyan") +
  geom_line(aes(y = button26), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Full Shade Grass",
    subtitle = "sensor3 (red), sensor16 (orange), sensor23(green), sensor25(cyan), sensor26(blue)",
    caption = "Figure 1"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

fullgrass <- fullgrass + theme(axis.text.x = element_text(angle = 45, hjust = 1))
fullgrass

```

### Full Shade Grass 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor3 <- as.numeric(aug2$sensor3)
aug2$sensor16 <- as.numeric(aug2$sensor16)
aug2$sensor23 <- as.numeric(aug2$sensor23)
aug2$sensor25 <- as.numeric(aug2$sensor25)
aug2$sensor26 <- as.numeric(aug2$sensor26)
aug2$ReportC <- as.numeric(aug2$ReportC)

fullgrass2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor3), color = "red") +
  geom_line(aes(y = sensor16), color = "orange") +
  geom_line(aes(y = sensor23), color = "green") +
  geom_line(aes(y = sensor25), color = "cyan") +
  geom_line(aes(y = sensor26), color = "blue") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Full Shade Grass (2pm)",
    subtitle = "sensor3 (red), sensor16 (orange), sensor23(green), sensor25(cyan), sensor26(blue)",
    caption = "Figure 2"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

fullgrass2 <- fullgrass2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
fullgrass2
```
## Full Soil 
### Full Soil 5AM
```{r}
fullsoil <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button5), color = "red") +
  geom_line(aes(y = button7), color = "orange") +
  geom_line(aes(y = button10), color = "green") +
  geom_line(aes(y = button12), color = "cyan") +
  geom_line(aes(y = button14), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Full Shade Soil",
    subtitle = "sensor5 (red), sensor7 (orange), sensor10(green), sensor12(cyan), sensor14(blue)",
    caption = "Figure 3"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

fullsoil <- fullsoil + theme(axis.text.x = element_text(angle = 45, hjust = 1))
fullsoil
```
### Full Soil 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor5 <- as.numeric(aug2$sensor5)
aug2$sensor7 <- as.numeric(aug2$sensor7)
aug2$sensor10 <- as.numeric(aug2$sensor10)
aug2$sensor12 <- as.numeric(aug2$sensor12)
aug2$sensor14 <- as.numeric(aug2$sensor14)
aug2$ReportC <- as.numeric(aug2$ReportC)

fullsoil2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor5), color = "red") +
  geom_line(aes(y = sensor7), color = "orange") +
  geom_line(aes(y = sensor10), color = "green") +
  geom_line(aes(y = sensor12), color = "cyan") +
  geom_line(aes(y = sensor14), color = "blue") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Full Shade Soil (2pm)",
    subtitle = "sensor5 (red), sensor7 (orange), sensor10 (green), sensor12 (cyan), sensor14 (blue)",
    caption = "Figure 4"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

fullsoil2 <- fullsoil2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
fullsoil2
```
## Partial Grass
### Partial Grass 5AM
```{r}
partialgrass <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button8), color = "red") +
  geom_line(aes(y = button34), color = "orange") +
  geom_line(aes(y = button35), color = "green") +
  geom_line(aes(y = button41), color = "cyan") +
  geom_line(aes(y = button45), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Partial Shade Grass",
    subtitle = "sensor8 (red), sensor34 (orange), sensor35 (green), sensor41 (cyan), sensor45 (blue)",
    caption = "Figure 5"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialgrass <- partialgrass + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialgrass
```
### Partial Grass 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor8 <- as.numeric(aug2$sensor8)
aug2$sensor34 <- as.numeric(aug2$sensor34)
aug2$sensor35 <- as.numeric(aug2$sensor35)
aug2$sensor41 <- as.numeric(aug2$sensor41)
aug2$sensor45 <- as.numeric(aug2$sensor45)
aug2$ReportC <- as.numeric(aug2$ReportC)

partialgrass2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor8), color = "red") +
  geom_line(aes(y = sensor34), color = "orange") +
  geom_line(aes(y = sensor35), color = "green") +
  geom_line(aes(y = sensor41), color = "cyan") +
  geom_line(aes(y = sensor45), color = "blue") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Partial Shade Grass (2pm)",
    subtitle = "sensor8 (red), sensor34 (orange), sensor35 (green), sensor41 (cyan), sensor45 (blue)",
    caption = "Figure 6"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialgrass2 <- partialgrass2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialgrass2
```

## Partial Soil 
### Partial Soil 5AM
```{r}
partialsoil <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button11), color = "red") +
  geom_line(aes(y = button32), color = "orange") +
  geom_line(aes(y = button36), color = "green") +
  geom_line(aes(y = button46), color = "cyan") +
  geom_line(aes(y = button61), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Partial Shade Soil",
    subtitle = "sensor11 (red), sensor32 (orange), sensor36 (green), sensor46 (cyan), sensor61 (blue)",
    caption = "Figure 6"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialsoil <- partialsoil + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialsoil
```


### Partial Soil 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor11 <- as.numeric(aug2$sensor11)
aug2$sensor32 <- as.numeric(aug2$sensor32)
aug2$sensor36 <- as.numeric(aug2$sensor36)
aug2$sensor46 <- as.numeric(aug2$sensor46)
aug2$sensor61 <- as.numeric(aug2$sensor61)
aug2$ReportC <- as.numeric(aug2$ReportC)

partialsoil2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor11), color = "red") +
  geom_line(aes(y = sensor32), color = "orange") +
  geom_line(aes(y = sensor36), color = "green") +
  geom_line(aes(y = sensor46), color = "cyan") +
  geom_line(aes(y = sensor61), color = "blue") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Partial Shade Soil (2pm)",
    subtitle = "sensor11 (red), sensor32 (orange), sensor36 (green), sensor46 (cyan), sensor61 (blue)",
    caption = "Figure 6"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialsoil2 <- partialsoil2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialsoil2
```

## Partial Shade Impervious

### Partial Impervious 5AM
```{r}
partialimp <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button38), color = "red") +
  geom_line(aes(y = button50), color = "orange") +
  geom_line(aes(y = button104), color = "green") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Partial Shade Impervious",
    subtitle = "sensor38 (red), sensor50 (orange), sensor104 (green)",
    caption = "Figure 7"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialimp <- partialimp + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialimp
```
### Partial Shade Impervious 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor38 <- as.numeric(aug2$sensor38)
aug2$sensor50 <- as.numeric(aug2$sensor50)
aug2$sensor104 <- as.numeric(aug2$sensor104)
aug2$ReportC <- as.numeric(aug2$ReportC)

partialimp2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor38), color = "red") +
  geom_line(aes(y = sensor50), color = "orange") +
  geom_line(aes(y = sensor104), color = "green") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Partial Shade Impervious (2pm)",
    subtitle = "sensor38 (red), sensor50 (orange), sensor104 (green)",
    caption = "Figure 8"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

partialimp2 <- partialimp2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
partialimp2
```

### Shade Grass
### Shade Grass 5AM
```{r}
shadegrass <- aug %>%
  ggplot(mapping = aes(x = Date, group = 1)) +
  geom_line(aes(y = button15), color = "red") +
  geom_line(aes(y = button17), color = "blue") +
  geom_line(aes(y = reportC), color = "black") +
  labs(
    title = "Shade Grass",
    subtitle = "sensor15 (red), sensor17 (blue)",
    caption = "Figure 9"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

shadegrass <- shadegrass + theme(axis.text.x = element_text(angle = 45, hjust = 1))
shadegrass
```

### Shade Grass 2PM
```{r}
aug2$August <- factor(aug2$August, levels = unique(aug2$August))
aug2$sensor15 <- as.numeric(aug2$sensor15)
aug2$sensor17 <- as.numeric(aug2$sensor17)
aug2$ReportC <- as.numeric(aug2$ReportC)

shadegrass2 <- aug2 %>%
  ggplot(mapping = aes(x = August, group = 1)) +
  geom_line(aes(y = sensor15), color = "red") +
  geom_line(aes(y = sensor17), color = "blue") +
  geom_line(aes(y = ReportC), color = "black") +
  labs(
    title = "Shade Grass (2pm)",
    subtitle = "sensor15 (red), sensor17 (orange)",
    caption = "Figure 10"
  ) +
  xlab("August Date/Time") +
  ylab("Temperature in C") +
  theme_bw()

shadegrass2 <- shadegrass2 + theme(axis.text.x = element_text(angle = 45, hjust = 1))
shadegrass2
```

## Part 2
```{r}
button <- read_excel("ButtonTiffNum.xlsx")
summary(button)
```

### Mean Albedo
#### Categorized by Shades
```{r}
#extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in the subset

mean(x=button$Albedo, na.rm = TRUE)
fullshade_data <- subset(button, Shade == "fullshade")
fullshade_avg_albedo <- mean(fullshade_data$Albedo, na.rm = TRUE)

partialshade_data <- subset(button, Shade == "partialshade")
partialshade_avg_albedo <- mean(partialshade_data$Albedo, na.rm = TRUE)

shade_data <- subset(button, Shade == "shade")
shade_avg_albedo <- mean(shade_data$Albedo, na.rm = TRUE)

shade_avg_table <- data.frame(
  Shade = c("fullshade", "partialshade", "shade"),
  Average_Albedo = c(fullshade_avg_albedo, partialshade_avg_albedo, shade_avg_albedo)
)
shade_avg_table
```

#### Categorized by GroundCover
```{r}
mean(x=button$Albedo, na.rm = TRUE)
grass_data <- subset(button, Ground == "grass")
grass_avg_albedo <- mean(grass_data$Albedo, na.rm = TRUE)

soil_data <- subset(button, Ground == "soil")
soil_avg_albedo <- mean(soil_data$Albedo, na.rm = TRUE)

imperv_data <- subset(button, Ground == "imperv")
imperv_avg_albedo <- mean(imperv_data$Albedo, na.rm = TRUE)

ground_avg_table <- data.frame(
  Shade = c("grass", "soil", "imperv"),
  Average_Albedo = c(grass_avg_albedo, soil_avg_albedo, imperv_avg_albedo)
)
ground_avg_table
```


### Mean Canopy
```{r}
mean(x=button$Canopy, na.rm = TRUE)
```

### Mean Elevation
```{r}
mean(x=button$Elevation, na.rm = TRUE)
```

## Regression (Aug 1 5AM)
```{r}
Canopy581 <- lm(AugTemp5am81~Canopy, data=button)
CanopyPAlbedo581 <- lm(AugTemp5am81~Canopy+Albedo, data=button)
CanopyMAlbedo581 <- lm(AugTemp5am81~Canopy*Albedo, data=button)
CanopyPElevation581 <- lm(AugTemp5am81~Canopy+Elevation, data=button)
CanopyMElevation581 <- lm(AugTemp5am81~Canopy*Elevation, data=button)
CanopyPElevationAlbedo581 <- lm(AugTemp5am81~Canopy+Elevation+Albedo, data=button)
CanopyMElevationAlbedo581 <- lm(AugTemp5am81~Canopy*Elevation*Albedo, data=button)
CanopyMElevationPAlbedo581 <- lm(AugTemp5am81~Canopy*Elevation+Albedo, data=button)
CanopyPElevationMAlbedo581 <- lm(AugTemp5am81~Canopy*Albedo+Elevation, data=button)

aic_values <- c(AIC(Canopy581), AIC(CanopyPAlbedo581), AIC(CanopyMAlbedo581), AIC(CanopyPElevation581), AIC(CanopyMElevation581), AIC(CanopyPElevationAlbedo581), AIC(CanopyMElevationAlbedo581), AIC(CanopyMElevationPAlbedo581), AIC(CanopyPElevationMAlbedo581))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table <- data.frame(
  Model = model_names,
  AIC = aic_values) %>%
  arrange(AIC)

print(aic_table)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.

#best fitted model: 
CanopyPElevation581 <- lm(AugTemp5am81~Canopy+Elevation, data=button)

CanopyPElevation581<- tidy(CanopyPElevation581, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyPElevation581 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  select(Term = term, Odds_Ratio = estimate, `p-value` = p.value, `95% CI` = conf.int) %>%
  kable(digits = 2, format = "markdown", caption = "Table 1: August1 5AM")
```

## Regression (Aug 1 2PM)
```{r}
Canopy281 <- lm(AugTemp2pm81~Canopy, data=button)
CanopyPAlbedo281 <- lm(AugTemp2pm81~Canopy+Albedo, data=button)
CanopyMAlbedo281 <- lm(AugTemp2pm81~Canopy*Albedo, data=button)
CanopyPElevation281 <- lm(AugTemp2pm81~Canopy+Elevation, data=button)
CanopyMElevation281 <- lm(AugTemp2pm81~Canopy*Elevation, data=button)
CanopyPElevationAlbedo281 <- lm(AugTemp2pm81~Canopy+Elevation+Albedo, data=button)
CanopyMElevationAlbedo281 <- lm(AugTemp2pm81~Canopy*Elevation*Albedo, data=button)
CanopyMElevationPAlbedo281 <- lm(AugTemp2pm81~Canopy*Elevation+Albedo, data=button)
CanopyPElevationMAlbedo281 <- lm(AugTemp2pm81~Canopy*Albedo+Elevation, data=button)

aic_values2 <- c(AIC(Canopy281), AIC(CanopyPAlbedo281), AIC(CanopyMAlbedo281), AIC(CanopyPElevation281), AIC(CanopyMElevation281), AIC(CanopyPElevationAlbedo281), AIC(CanopyMElevationAlbedo281), AIC(CanopyMElevationPAlbedo281), AIC(CanopyPElevationMAlbedo281))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table2 <- data.frame(
  Model = model_names,
  AIC = aic_values2) %>%
  arrange(AIC)

print(aic_table2)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.


#best fitted model: 
CanopyMElevationAlbedo281 <- lm(AugTemp2pm81~Canopy*Elevation*Albedo, data=button)

CanopyMElevationAlbedo281 <- tidy(CanopyMElevationAlbedo281, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyMElevationAlbedo281 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  select(Term = term, Odds_Ratio = estimate, `p-value` = p.value, `95% CI` = conf.int) %>%
  kable(digits = 2, format = "markdown", caption = "Table 2: August1 2PM")

```
## Regression (Aug 2 5AM)
```{r}
Canopy582 <- lm(AugTemp5am82~Canopy, data=button)
CanopyPAlbedo582 <- lm(AugTemp5am82~Canopy+Albedo, data=button)
CanopyMAlbedo582 <- lm(AugTemp5am82~Canopy*Albedo, data=button)
CanopyPElevation582 <- lm(AugTemp5am82~Canopy+Elevation, data=button)
CanopyMElevation582 <- lm(AugTemp5am82~Canopy*Elevation, data=button)
CanopyPElevationAlbedo582 <- lm(AugTemp5am82~Canopy+Elevation+Albedo, data=button)
CanopyMElevationAlbedo582 <- lm(AugTemp5am82~Canopy*Elevation*Albedo, data=button)
CanopyMElevationPAlbedo582 <- lm(AugTemp5am82~Canopy*Elevation+Albedo, data=button)
CanopyPElevationMAlbedo582 <- lm(AugTemp5am82~Canopy*Albedo+Elevation, data=button)

aic_values3 <- c(AIC(Canopy582), AIC(CanopyPAlbedo582), AIC(CanopyMAlbedo582), AIC(CanopyPElevation582), AIC(CanopyMElevation582), AIC(CanopyPElevationAlbedo582), AIC(CanopyMElevationAlbedo582), AIC(CanopyMElevationPAlbedo582), AIC(CanopyPElevationMAlbedo582))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table3 <- data.frame(
  Model = model_names,
  AIC = aic_values3) %>%
  arrange(AIC)

print(aic_table3)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.


#best fitted model: 
CanopyPElevation582 <- lm(AugTemp5am82~Canopy+Elevation, data=button)

CanopyPElevation582<- tidy(CanopyPElevation582, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyPElevation582 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  select(Term = term, Odds_Ratio = estimate, `p-value` = p.value, `95% CI` = conf.int) %>%
  kable(digits = 2, format = "markdown", caption = "Table 3: August2 5AM")
```

## Regression (Aug 2 2PM)
```{r}
Canopy282 <- lm(AugTemp2pm82~Canopy, data=button)
CanopyPAlbedo282 <- lm(AugTemp2pm82~Canopy+Albedo, data=button)
CanopyMAlbedo282 <- lm(AugTemp2pm82~Canopy*Albedo, data=button)
CanopyPElevation282 <- lm(AugTemp2pm82~Canopy+Elevation, data=button)
CanopyMElevation282 <- lm(AugTemp2pm82~Canopy*Elevation, data=button)
CanopyPElevationAlbedo282 <- lm(AugTemp2pm82~Canopy+Elevation+Albedo, data=button)
CanopyMElevationAlbedo282 <- lm(AugTemp2pm82~Canopy*Elevation*Albedo, data=button)
CanopyMElevationPAlbedo282 <- lm(AugTemp2pm82~Canopy*Elevation+Albedo, data=button)
CanopyPElevationMAlbedo282 <- lm(AugTemp2pm82~Canopy*Albedo+Elevation, data=button)

aic_values3 <- c(AIC(Canopy282), AIC(CanopyPAlbedo282), AIC(CanopyMAlbedo282), AIC(CanopyPElevation282), AIC(CanopyMElevation282), AIC(CanopyPElevationAlbedo282), AIC(CanopyMElevationAlbedo282), AIC(CanopyMElevationPAlbedo282), AIC(CanopyPElevationMAlbedo282))
model_names <- c("canopy", "+albedo", "*albedo","+ele", "*ele", "+ele+albedo", "*ele*albedo", "*ele+albedo","*albedo+ele")
aic_table3 <- data.frame(
  Model = model_names,
  AIC = aic_values3) %>%
  arrange(AIC)

print(aic_table3)
#The lower the value for AIC, the better the fit of the model. The absolute value of the AIC value is not important. It can be positive or negative.


#best fitted model: 
CanopyPElevationAlbedo282 <- lm(AugTemp2pm82~Canopy+Elevation+Albedo, data=button)

CanopyPElevationAlbedo282 <- tidy(CanopyPElevationAlbedo282, 
                     conf.int = TRUE, conf.level = 0.95)
CanopyPElevationAlbedo282 %>%
  filter(term != "row1") %>%
  mutate(conf.int = paste0("(", round(conf.low, digits=2), ", ", round(conf.high, digits=2), ")")) %>%
  select(Term = term, Odds_Ratio = estimate, `p-value` = p.value, `95% CI` = conf.int) %>%
  kable(digits = 2, format = "markdown", caption = "Table 4: August2 2PM")

```

